\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-04 paper.tex
6. Attempt to clean up Public Good introduction.

I will take two approaches to arguing that the public good is being upheld. First will be a purely numerical approach to public good, `` ``Public Good'' By The Numbers'', followed by an argument that the public good is not only being upheld, but improved by World of Warcraft, `` ``Public Good'' Being Improved''.

>>>>

First will be a purely numerical, Utilitarian approach to public good, `` ``Public Good'' By The Numbers''. I find this argument to be a bit heartless and cold and so I will follow it with a section that shows that the public good is not only upheld, but improved, by World of Warcraft, `` ``Public Good'' Being Improved''.
